---
title: "MR beta compare between DICE and oneK1K"
author: "ling"
date: '2022-12-20'
output: html_document
---
## Overview
We aim to compare the beta value of MR results in DICE and oneK1K datasets. The matching criteria is "gene-cancer-cell type". We select B cell naive cell type for compare.
Analysis1 is for DICE top findings, Analysis2 is for DICE all MR results.

## Analysis1
### Datasets1
DICE has 973 top findings (MR+coloc evidence) , we select the top findings in B cell naive, we got 65 results for compare.
We detect no gene_B cell naive pairs of DICE top findings in oneK1K top findings, so we use all MR results in oneK1K with the same gene_B cell naive pairs. We have 273 results for compare.
We match the two compare datasets with the matching criteria

```{r}
library(ggplot2)
setwd("/Users/tq20202/Desktop")
dice<-read.csv("dicetop_bcell.csv")
head(dice)
onek1k<-read.csv("onek1k_bcell.csv")
head(onek1k)
i<-intersect(dice$m,onek1k$m)
test<-data.frame(id=i,dice_beta=dice[dice$m==i,"b"],onek1k_beta=onek1k[onek1k$m==i,"b"])
test
```
we only got one result in same direction

## Analysis2
### Datasets2
we then select DICE all MR findings in B cell naive, 12183 results total
oneK1K select all MR results in B cell naive,1420 results total
match the two datasets with the matching criteria,378 matched results total for plotting

```{r}
f=list.files("/Users/tq20202/Desktop/DICE2/mrres")
data<-c()
for (i in 1:length(f)){
  temp<-read.table(file=paste("/Users/tq20202/Desktop/DICE2/mrres/",f[i],sep=""), header=T, sep="\t", quote="", stringsAsFactors=F, check.names=F)
  temp$gene<-sapply(strsplit(as.character(temp$id),'_'), "[", 1)
  temp$cell<-sapply(strsplit(as.character(temp$id),'_'), "[", 2)
  temp$cancer<-strsplit(f[i],split = "_")[[1]][2]
  temp<-temp[temp$cell=="B cell, naive",]
  data<-rbind(data,temp)
}
data$m=paste(data$gene,data$cancer,sep="_")

f=list.files("/Users/tq20202/Desktop/oneK1K/mrres")
data2<-c()
for (i in 1:length(f)){
  temp<-read.table(paste("/Users/tq20202/Desktop/oneK1K/mrres/",file=f[i],sep=""), header=T, sep="\t", quote="", stringsAsFactors=F, check.names=F)
  temp$gene<-sapply(strsplit(as.character(temp$id),'_'), "[", 1)
  temp$cell<-sapply(strsplit(as.character(temp$id),'_'), "[", 2)
  temp$cancer<-strsplit(f[i],split = "_")[[1]][2]
  temp<-temp[temp$cell=="Naïve/Immature B Cell",]
  data2<-rbind(data2,temp)
}
data2$m=paste(data2$gene,data2$cancer,sep="_")
i<-intersect(data$m,data2$m)
dice<-data[data$m %in% i,]
dice<-dice[order(dice$m),]
onek1k<-data2[data2$m %in% i,]
onek1k<-onek1k[order(onek1k$m),]
dd<-data.frame(beta_dice=dice$b,beta_oneK1K=onek1k$b)
head(dd)
```

## scatter plot

```{r}
ggplot(data = dd, mapping = aes(x = beta_dice, y = beta_oneK1K)) + geom_point(size = 3, alpha=0.3)
```

## conclusion
The beta value of MR results in DICE and oneK1K datasets seems not very consistent
